---
title: "Weight of Fish"
author: "Wesley cruz"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight

```{r}
fish <-read.csv(file="Fish.csv",header=TRUE)
```

## Perch

```{r}
Perch <- filter(Fish, Species=="Perch")
Perch <- select(Perch, -(Species))
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

### Best Two regressor model

```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```

The models shown above are designed using the r command to explain how to predict the weight of a Perch fish. The first graph reveals that the most suitable model for this fish is also the top two-regressor model. We then move on to the "Best Two Regressor Model" command and identify that the two-component model employs the statistical variations between the factors that contribute to predicting the weight of a Perch fish. This is the reason height and width appear at the top of the initial command. The adjusted r-square value stands at 0.940 on the y-axis, while the most fitting and best two-regressor model is plotted at the second x-axis value.


## Pike

### Best Models

### Best Two regressor model

## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements