---
title: "Weight of Fish"
author: "Wesley cruz"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight

```{r}
fish <-read.csv(file="Fish.csv",header=TRUE)
```

## Perch

```{r}
Perch <- filter(Fish, Species=="Perch")
Perch <- select(Perch, -(Species))
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

### Best Two regressor model

```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```

The models shown above are designed using the r command to explain how to predict the weight of a Perch fish. The first graph reveals that the most suitable model for this fish is also the top two-regressor model. We then move on to the "Best Two Regressor Model" command and identify that the two-component model employs the statistical variations between the factors that contribute to predicting the weight of a Perch fish. This is the reason height and width appear at the top of the initial command. The adjusted r-square value stands at 0.940 on the y-axis, while the most fitting and best two-regressor model is plotted at the second x-axis value.


```{r}
best_Perch_Model <- lm(Weight~Height+Width,data=Perch)
five_element_perch_model <- lm(Weight~.,data=Perch)
anova(best_Perch_Model, five_element_perch_model)
```

The Analysis of Variance presented here demonstrates the probability of the two-element model being significant. This is why the difference in RSS values between the two-element model and the five-element model is minimal. Model 1, derived from height and width, has an RSS value of 384,478, while Model 2, which takes into account Length1, Length2, Length3, Height, and Width, has an RSS value of 379,369.

## Pike

```{r}
Pike <- filter(Fish, Species=="Pike")
Pike <- select(Pike, -(Species))
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topleft",main="Adjusted R^2")
```

The r command responses display the optimal model for predicting the weight of Pike fish based on the data used. The subset size constitutes the x-axis, and the adjusted R-squared value forms the y-axis. The legend conveys the significance of the highest plot, "L1-L2-L3-H-W." The plot's importance is highlighted by its position as the best model for predicting Pike weight, which is why it is placed above the others. The adjusted R-squared value associated with this model is 0.975.

### Best Two regressor model

```{r}
Pike_best.model <- lm(Weight~.,data=Pike)
summary(Pike_best.model)
Pike_best_2_R_Model <-lm(Weight~Length1+Length3, data=Pike)
``` 

The ANOVA output generates the analysis we require to scrutinize our hypothesis. Through employing ANOVA, we determine that the p-value is 0.03091, making it significant since it falls below the 0.05 threshold. The ANOVA output compares the optimal model with the two-element model, which explains why Model 1 encompasses all elements for predicting Pike weight, and Model 2 only contains two elements for prediction purposes.

## Roach
```{r}
Roach <- filter(Fish, Species=="Roach")
Roach <- select(Roach, -(Species))
```

### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomleft",main="Adjusted R^2")
```
We acquired the data for this fish from the files, and the r command generated the optimal prediction approach. The graph concurs that the best model is the two-element model, as it surpasses the other models. This finding resembles the Perch results, where the top model is also a two-element model. In this particular graph, the highest-ranking one-element model is above 1, the best two-element model is above 2, the best three-element model is above 3, and so forth.

### Best Two regressor model

## Final Summary Statements